Delayed effects of climate on vital rates lead to demographic divergence in Amazonian forest fragments

### 2021-06-28 doc/paper.Rmd
pdf versions of figures

@@

@@

@@

@@

@@

>>>>

```{r eda_vect, fig.height=7, fig.width=7, dev='pdf', include=FALSE}
tar_read(eda_plot) & theme(text = element_text(size = 10))
```

@@

```{r surv-curve_vect, fig.height=3.5, fig.width=7, dev="pdf", include=FALSE}
tar_read(surv_curve) + theme(text = element_text(size = 10))
```

@@

```{r size-plot_vect, fig.width=7, fig.height=7, dev='pdf', include=FALSE}
tar_read(size_plot) & theme(text = element_text(size = 10))
```

@@

```{r surv-spei_vect, fig.height=7.5, fig.width=7, dev='pdf', include=FALSE}
tar_read(s_spei_plot) & theme(text = element_text(size = 10))
```

@@

```{r growth-spei_vect, fig.height=7.5, fig.width=7, dev='pdf', include=FALSE}
tar_read(g_spei_plot) & theme(text = element_text(size = 10))
```

@@

```{r flwr-spei_vect, fig.height=7.5, fig.width=7, dev='pdf', include=FALSE}
tar_read(f_spei_plot) & theme(text = element_text(size = 10))
```
